Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain body_used

\subsubsection{body_used}
\label{subs:body_used}

>>>>

\subsubsection{body_used}
\label{subs:body_used}
Additionally to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}). The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines. It is also acceptable to use bullet points. This criterion only checks if there is a body.
